\documentclass[]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amsmath,amssymb,stackengine,xcolor}
%opening
\title{You}
\author{Andreas S. Erslev}
\renewcommand{\abstractname}{You}
\begin{document}

\begin{center}
	\Large\textbf{You}
\end{center}
\begin{center}
	\large\textbf{Andreas S. Erslev}
\end{center}

\begin{center}
	\large\textbf{1. Her}
\end{center}

She had already opend her eyes. *Click* *Click* said the alarm. She let it click. It drove her mother crazy. "Oy, Jenny, stop the bloody ruckus". It gave her a deviant smile. The clicking became a clapping. The commotion stoped. She got up. Made her bed. Put on the outfit, se had so carefully laid out the day before. Looked in the mirror. "This is the perfect mask" she thought to herself. "Oy, Jenny, u better get ya arse down here. Ah' can't wait all bloody day." Breakfest, the usual. Toast. fried eggs. Fresh juice. A cup of coffee. Or tea. Her morning was just like a boring reincarnation.
\\ \\
TL;DR: Morning. Rituals. Traditions.
\\ \\
She left. Time for school. Same old, same old. The fat kid in class, that couldn't climb the rope. So much fat, so much weight. The muscle guy who couldn't do it either. So much muscle, so much weight. It was the same every thursday. Sometimes new games. But the new games became old. A short lifespand. Every other day, different stories, same conclusion. 
\\ \\
TL;DR: School. recurrence. reiteration.
\\ \\
She was a loner. Not many could match her compatability. However, social intelligence wasn't something she was laking. Normally it wasn't worth using. But she needed help. Especially a false blame. She wanted to make a fool out of the principal. Just like so many others. He had taken her off the spelling bee team. Reckless behavior. And the fact, that she couldn't spell. Soon, he would stand naked, tied up, with red splattert tomato viscera flowing down his face. Crumpled, with center around the ocean blue groin. Once again, success.
\\ \\
TL;DR: Revange. Habits. Patterns.

\newpage

\begin{center}
	\large\textbf{2. Him}
\end{center}

He was a rascal. Black leather jacket and a bubble gum ciggy behind the ear. Black shiny oily hair. Thight blue jeans. A white t-shirt, with a empty pack of Lucky Strike pressed up the sleeve. Spitting, like he was chewing tobacco. Howling at the younger. Smoking oregano. Sunglasses, even on a foggy day. A newlyborn punk. He hanged with his crew. Oh yes, all the baddest of boys. Oooohh no, you wouldn't want to bring this tuff guy home. Not exactly mother in law compatible. 
\\ \\
He came from a great home. A father, working with passion, at a dead end 9 to 5. A mother, working with a smile on her face, at their blank estate. Dinner was servered at 6:30, sharp. Home cooked everyday. With the exception of friday. Two number 9s, a number 9 large, a number 6 with extra dip, a number 7, two number 45s, one with cheese and larges sodas. Flowing in fat and carbondioxide. Two sisters, one older and one younger. Both pretty. The older, an aspiring woman, the younger, an angel. He was attracted to her. Penis pleasure. It was wrong. He liked that.
\\ \\
He had gotten a fake ID. Beer and smokes. Down to the local shop, with his newly grown puberty beard. "A six-pack and a pack of Lucky Strike, please" he said, with a shakey teenage transitional voice. "Mate, you gotta get it ya'self. You think this is a fucking resutrante?" said the acne harassed cashier. Frightened, he walked down the aisles. He picked one. The one with mermaids. Pizza-face didn't scan the goods. Without even looking at the ID, Mr. Rosacea said "Okay, that'll be 11.67". He was shocked. His allowance didn't allow it. "Give me a minut" he said with a pale face. He went outside to cadge from the other tossers. Went back ind. And came back out. "Fuck me dead. We bloody got it lads" he proudly spad out, with saliva thrown down the chin. "Taking the piss?" they all yelled, ignoring the spit in their eyes. Mission succsessfull.

\newpage

\begin{center}
	\large\textbf{3. Those two}
\end{center}

\begin{center}
	\textbf{3.1. A unfamiliar glance "A new begining"}
\end{center}

They had grown older. Him moreso than her. He had a outgrown puberty beard. Her, with her deviant smile on her lips. 
\\ \\
A bloody mary on the bar counter. A half sheet celery dangling from her mouth. A seductive glance from her eyes. Scouting the room for fun experiences. Many men. Many bellys flowting over the belt. Smokey words and ember eyes. She wasn't like the others. With her long red glowing dress and hair done for hours. Exactly how she wanted it. The perfect mask. 
\\ \\
He came through the door. Smacking it so hard, that the dart arrows fell from bulls eye, to the depths of an garbage bin. An unusually weird place for a garbage bin. His glance scouted the room. Right passed her. He went for the pool table. Startet hustling the poor common men. She was annoyed. She needed attention. 

\begin{center}
	\textbf{3.2. A alternating her}
\end{center}

I watched him. He lost again and again. I was annoyed. He didn't even look. Properbly gay. I never converted a gay man. Oh, well, one time should be the first. So I watched him a bit more. Looked for his soft spot. But it seemed as if he didn't have any. No entry point. Hm. I went to the table. Pulled my dress up to the thigh, and straped it with a fat mans belt. "Okay bois, are you ready to loose to a girl?" I asked, like a stripper, pushing her breasts against her customors face. Jaws droped, as I went down for the balls, and revealed my pink panties. Execpt for lether boy. Not even a glance. "I'll play ya" he said, not even looking at me. 
\\ \\
To make a long game short, I lost.

\begin{center}
	\textbf{3.3. A old him}
\end{center}

I watched her pride crackle off. Her ember eyes killing me in thousand ways. "Well love, you wanna go 2 outta 3?" I said with exultant tones. She left with anger floating out every hole. Straigt to the pisser. I continued my hustle. Trippled the amount, and called it a day. I glanced at the shitter. I noticed she hadn't come out yet. Must be a long shite. I went to check on her, such a fragile woman, in the wrong part of town. "Oy, maam, u alright in'ere?" I yelled. She banged the door open, startet to stab me with a rather hard pencil. "Bloody'ell maam, wha' ya doing". She stopped, gasping for air. "you got a ciggy?" she asked, as the pencil hit the floor. 

\begin{center}
	\textbf{3.4. A unchanged them}
\end{center}

This was the begining of two lovers journy trough the years. Money for unholy jobs. Always on the run. Drugs floating through the vains. Alcohol as a replacement for blood. They did everything together, him with a ciggy in his mouth and her with a devient smil on her lips. The years went by, and as his beard grew longer, her rinkels stayed away. They had grown older. Him moreso than her. They needed to settle down. 
\\ \\
They went to a small town, with lovely nature, exluded from the rest of society and a river floating down the middle. They met a man. They helped him, he helped them and soon they were of the radar. They had gotten a more or less normal life. Bloodcells comming back, slowly and tar leaving the body. But don't think they left the wild side behind. Dependency of adiction were still very much part of their image.

\begin{center}
	\textbf{3.5. A new you}
\end{center}

One day, something odd happend with him. He trimmed his beard. I had never seen him, without just a bit of stubble. "What's wrong?" I asked, worried. "I just needed a bit of change, love." he said, with sinister tones. "Let's go to the pub". So they did. Had a pint. A bloody mary. Cash floaing over the barcounter. "Another, *hirk*, my good sir". The dawns ember became dusks ash. "Let's get a bit extra" he said. She agreed. "What you got?" "LSD" "LSD it is". They started tripping. 
\\ \\
They went home. "Let's have sex" he said unsexy. He started to tie her up to the chair, even before she could awnser. He taped her head, so she couldn't move. He got a knife. Blood floated down her face, as he draged it down, slowly, again and again, creating newborn scars. She didn't scream. If this what was he wanted, this was what he shoul get. He got up. And left. She sat there for days. He was gone. A new name. A new life. A new her.

\newpage

\begin{center}
	\large\textbf{4. Them}
\end{center}

She was broken. She was beaten. She was bleeding. She was hungry. She was cold. She was lost.
\\ \\
Sitting in the chair, naked, screaming silently. The building caretaker came by. He had to check the radiator. He quickly untied her and went to call the police. She stoped him. She didn't want him to get in trouble. She was mentally locked in his basement in Stolkholm. She was, however, angry. She slaped the caretaker, because he was a lonely man. Masterbating to loud porn, that had kept her awake several nights. She pulled him to bed. They had soundless sex. Just for a short moment. He died, as the semen sprayed her face pale, covering the bloody wounds. A weak lonely heart. What a delightful feeling. She liked the pale look. A perfect mask.
\\ \\
She wandered dumbfounded around. Trough the streets. Red lights striking her face. Naked ladys dancing around poles, suitored by fat lonely men. She felt the sexuall fog. The sexual vibrations trough the air, aiming for the poor women. Non returned. A man offered her money. She just had to place her bare arse on his pate. So she did. She started to slowly press it down over his face. She could feel his cold breath on her cunt. She placed her legs on his arms. He couldn't move. Slowly he suffocated, sparkling with his legs. A delightful feeling, as his boody went numb. Like all his senses faded away, one at a time. The wind on her puzzy disappeared. 
\\ \\
The owner came down. "Take this, and stay silent in the back, NOW!". He thought she worked there. She went in the back, as she vaguely heard the word "cunt" thrown in her back. They wondered who she was. She took some wet wipes, and pealed the pale mask of her skin, reviling the stripes running down her face. "I will make a pagt with the dark ones. I will stop the horny male epidemic. I will go the way of the sirens. I will lure them to darkness, the depth of the waters. I will". Some of the girls, fled out the room. Some stayed. Soundless clapping. They should meet again. She left. She went home. The chair was gone.
\\ \\
She had found an abandoned ark. Cheap. She bought it. They arrived at berth 13. She stood on a chair. She had an old rusty knife. "If you want to change the world, you have to change yourself!" she yelled at the top of her lungs. "Join me, and we will rule the man kind. If you are ready, take this knife, and give yourself the symbol of a siren!". They took the knife, slicing clean cuts down their faces. They were spellbound by their leader. She started singing. They started singing. She couldn't sing. They couldn't sing. She became accepted by the grey witches. They became accepted by the grey witches. She could sing. They could sing. She was given the name. They became nameless.

\newpage

\begin{center}
	\large\textbf{5. You}
\end{center}

I saw you. Leaving appertment eleven. You looked happy. In your hand, a black woman. Funny. You used to be a racist. She was so barsk. Fat, bleached hair and lips the size of a baboons arse. You didn't have a beard. Not even stubbles. I followed them. Stayed my distance. They parted ways. She continued. He stopped. Waiting for the bus. Funny. You used to hate the bus. I got myself a cab. The bus stopped. He got out. Into a Ikea. Funny. You used to hate furniture. Except for that awfull chair. He came back out. With a Billy.
\\ \\
I stalked him for days. Learning his every move. Forgetting about my sworn duty. The others reminded me. I wanted him. They needed me. I realized, I was in his basement in Stolkholm. I needed out. I had a plan. I told the others. How he started it. How he was my goal. My puppeteer. They understood. He had to go. Just like the others. I collected everything from our past life. We starlked her. She talked to her. She meet her. She showed her. I saw her broken shit brown eyes soaking. I laught. She ran away. I smiled, as he came home late at night, to an empty bed. I waited all night. He came out. Walking like a zombie. It was done. A lonely broken hearted man.
\\ \\
Days went by. I watched him everyday. She got ready. With her long glowing red dress and hair done for hours. She sang the same song again and again. The song she had to sing. He came out. He went down the street. Destination, "The Flirtatious Succubus". Now was the time, if ever. We waited. She went in. They went home. I waited. Time went by. She came out. With him as her puppet. She took him home. Spellbound by her singing. I watch them. They went in. I waited. Time went by. They all came out. With him as their puppet. They took him to berth 13. Speelbound by their singing. They boarded the ark. I waited. Time went by. They came back down. I boarded. You were under the ice. I reached down. You grabed me. I looked at you. You screamed. I laughed last. The end of you and I.

\end{document}
