\documentclass[]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amsmath,amssymb,stackengine,xcolor,graphicx}
\graphicspath{ {./images/} }
%opening
\title{Water}
\author{Andreas S. Erslev}
\begin{document}

\begin{center}
	\Large\textbf{Lies and Snake-Eyes}
\end{center}
\begin{center}
	\large\textbf{Andreas S. Erslev}
\end{center}

\begin{center}
	\large\textbf{1. On a first name basis}
\end{center}

Hi. My name is Jill. I lie. I'm a compulsive liar. I lie, cause it's fun to see, how much bullshit you can make a man bealive. I lie mostly to men. To get them in bed. Or make stories, they'll be telling their lads about. To make them buy me drinks. To make dem do my bitting. I love control. I love making people think they're safe. But no. They are never safe, when they are with me. Cause I have a seacret. So let me tell you the story of my seacret. I guess it won't be that seacret anymore. But I promise you, that this story is true.
\\ \\
The real story begins, with a man called Jack. But before the real story can begin, we first need a bit of information. We need to prepare for the story, like one would prepare for a test, back in school. And as always with a test, there will be questions asked, that we haven't prepared for. So, to start of my story, let's start with the main character. Me.

\begin{center}
	\large\textbf{2. Let me tell you about my past}
\end{center}

As little, I was a true Missus Goody Two Shoes. I always told the truth. This went until I met Jack. But we will get to that, when we are ready. I was a rather intelligent litlle girl. One you would normally call a geek. I did have friends, I wasn't alone in the world, but I was an easy tarked for those, who had to show dominans. It didn't bother me at first, but as I got older, and nothing changed, it started to get on my nerves. Especially cause non of my friends even considered doing something.
\\ \\
Parents weren't to much help, either. "Just ignorer them" they said "Then they will get bored eventually." Well, it isn't that easy to ignorer a wedgie. And later on, getting your head stuck in a toilet. Times were rough, but I had to push through. I found peace in doing homework. Taking tests. Improving purly intellectually. I wanted to become a scientest. Or a doctor. Something with a high status, so i could finally show the world, what I was made of.
\\ \\
As I grew older, my passion for knowledge didn't fade. I, however, did get an urge to evolve socially. I started to branch out. Try getting out of my normal, secure friends cirkel. So I hopefully would stop being bullied. This should seem to be harder, than first expected. Talking to the "cool kids" had some rules. It was cool, if you smoked. You needed the right cloths. You needed the right slang. Everything was so different, from what I was used to. So I did the only thing I could do. I became a chameleon. 
\\ \\
I started smokeing secretly, even though it wasen't easy. I studiet the slang they seemed to use. I learned the rules of all the sports, that where prioritized. I started making a look, that was so different, that I would look like a new girl. So they wouldn't recognize me. The plan was set. Now, to put it in action. My stomach was full of butterflies. I couldn't think straight. I had been stressing so hard, with all the preparations and homework I had done, the last couple of weeks. What if it didn't work? I had to try.

\begin{center}
	\large\textbf{3. First day of school}
\end{center}

*Click* *Click* The clicking noice from the arlarm set the day of. Eyes open. Body frozen. Today was the day. Make up. New cloths. Shoes tied. Legs walking. Hair fluttering. determination determined. I walked staright up to Tom, the quarterback of the home team. "Hello there!" I said, with a bit shivere in my voice. "Ehhh, hello. Do I know you? Maybe from a party or something?" Tom wasn't the part of the group, that had bullied me. Those were loosers. Tom was definitely not a looser.
\\ \\
I lied. He knew nothing of me. I knew everything about him. I was a ghost in his eyes. Well, I was a ghost. Not anymore. "Yeah, we met at a party, not to long ago. But jus shortly. A quick hallo and a handshake, and the you were off. Tom was it?" I said calmly. I was a natural bone liar. Not a thing in my voice, my exprestion, my body language could give me away. "Oh, well, sorry, i don't remember. What's you name again?" he said, with a bit of a confused tone in his voice. "Jill. My name is Jill. Nice to meet you, Tom. For real this. time."
\\ \\
It worked. Tom seemed nice, and was very accommodating. He quickly  introduced me to his group of friends. No one suspected a thing. I told them, that I had been a quiet girl. But after a near death experience, I wanted to experience the world. First thing on my bucket list, were making new friends. Lies are best, when they stick to the truth. "My granmother and I where driving in USA. As you might imagine, my grandmother isn't exactly Vin Diesel slowly we mounted a small hill. As we pass a corner, a grown bison came running right next to us. Almost ran directly into the car. A bison that size would crash the car, and throw us off the raod. A certain death. Luckely it ran past us."
\\ \\
The story had made my interessting. "Oh god Jill, what a story", "What an experience", "wow, i'd really like to visit America, and see animals like bisons and surikats." I was a hit. The following days, i met with the gang at school. Had lunch with them, hanged out doing breaks, smoked lucky strikes behind the dumster. But it all went south, a thursday morning. The bullies reconized me.
\\ \\
As the months went by, I started to care less about school, and more about the gang. The years passed on, and the drinking and smokeing became worse and worse. We faked ID's and went to bars. We skipped school, to smoke weed. I was going down the wrong passage.
\\ \\
After I finished high school, collage was wating. I got good grades, and was accepted into a good school. This was the town I met Jack.

\begin{center}
	\large\textbf{4. The begining of my story}
\end{center}

Jack was a simple low life. A criminal doing small crimes. Did a small bit of time, over a couple of episodes, but nothing serious. I met him at a bar. The Delinquent Palas Nomen. He was good at talking. Very articulat. He had a day job as a telemarketing salesman. He was pretty good at the job, but he boss had an ambivalent opinon about him. At one side of the LP, he did the most sales. On the other side, he didn't show up half of the time.
\\ \\
He was a regular at The Delinquent Palas Nome. I was a semi regular. One of the bars that never asked for ID. had a deal, with the local police. A bloody mary. That was my drink. I was called Medusa, by the bartender, as every man froze a bit, the first time they saw me. But not Jack.
\\ \\
That made my interest in Jack quite strong. A man that could resist my pure sexual power? A man that could talk the panties of a woman. "A perfect match" I thought to myself. "No one could get close to us" I continued. We taled for about thirty minuttes. Then to the bathroom. He was good. Different. 
\\ \\
He pulled my skirt up, ripped my underpants apart, and thrusted his erect penis up my vargina. He had talked me wet. He knew this. With my hands pushed up a wall and my body swinging for every shock. As a dog, he was my master. He swung me around, position to position. Suddenly his finger was in my arse. I had never tried it. I had always been afraid. It hurt. But it was okay. He could do what he wanted. Orgasme upon orgasme. Until he oushed me to my knees, pounded his schlong deep down my throat, and shot his load right down my throat. I almost choked, but survied in the end. As I was coughing, he left the bathroom. Went out in the bar, and found a new group of people to talk too.
\\ \\
The next few months went by, as I almost daily was punding bloodymaries down my throat. Listing to Jack's stories. Figuring out, how to seduse him. Waiting patiently to strike down upon him. School didn't matter. That evaning with Jack, was the only thing on my mind! The day was today. He talked about the crimes he had done, mostly, he was so proud of it. So the last few weeks, i'd been selling dope at the school. I had broken into the libary, to stell the computer. I had hustled money from people around town. 
\\ \\
"Hay sailer, remember me?" I said with the most seducing voice I could make. "No". he said, with a voice as cold as ice, and turned his head. I had to do something else. Something extraordinaire. I had to make a coup. He always talked about the time he robed a kiosk. So I thought to one up that accomplishment. For days, I planed and planed. Slowly collected a crew from the bar. A driver, Magnus. A gunner, Hank the tank. A collector, Charlie, short for Charles. All I needed now, was Jack

\begin{center}
	\large\textbf{5. The point no return in my life. \newline And in the story}
\end{center}

Luckely for me, the word about my plan spread out through the bar. The word reached Jack. I had positioned me at the table next to his. With my crew. Drinking a Bloody Marie. Talking loud, about how we needed one last man. I discribed the man to be like Jack. After I'd talked for an hour, or so, he grabed me, put a ciggeret in my mouth, and took me outside. "I can do it!" he said with commitment "I know I can!". I pretended that I wasn't sure. That I wasn't impressed. Even though I was dying of joy inside. After ten minuttes, I agreed.
\\ \\
Now to set it up. We planed the perfect day. A monday. The day of the week, with the smallest amount of cusomers. 10:30 a.m. The time with the the smallest amount of The bank was out on the country side. The police station were far away. A seacret alarm. 2 staff members. Glass doors. That was the biggest problem, as the public would be able to see us make the robbery. We had masks. We had guns. We had a bag. We had a van. We had 2 minuts. We had it all.
\\ \\
We rolled up. I gave a pep-talk. masks on. Guns ready. We ripped the door open, Charlie fell, We ran inside, "THIS IS A MOTHER FUCKING STICK UP, HANDS IN THE AIR, OR BULLETS IN THE FACE! STAY AWAY FROM THE ALARM BUTTON YOU FUCKING BITCH!" the Tank yelled, at the top of his longs, charlie came runing, put his 9 mm. in the woman behind the desk's face, "GIVE ME ALL THE FUCKING MONEY, NOW NOW NOW" Charlie yelled, the Tank went around collecting ID's of everybody, so if they would snitch, we would know who they were, and how to find them, and thretend to kill them all, *BANG* it sounded, as I shot a warning bullet in the air, the Tank took as a sign, and capped an old woman, blood splattered all over the place, as my mind can only think about Bloody Marie's, the money is collected, thirty seconds before time ran out, running towards the van, jump in, "DRIVE YOU FUCKING WANKER!" Jack screeamd in panick, Charlie fell again as the van accelerated, and became unconscious. 
\\ \\
We got the money. We waited two weeks, under the radar. Non of us met. Not even at The Delinquent Palas Nomen. After the two weeks had passed, we met. We split the money. Another three weeks passed by. No police. No one knew who we were, where we came from or how to find us. the mission was a succsed. As we meet at The Delinquent Palas Nomen, joy and drinks were passed around the bar. After the 5 weeks, Jack was looking at me, in another light. 

\newpage

\begin{center}
	\large\textbf{6. Getting new acquaintances and a new profession}
\end{center}

One day, a man showed up at the bar. Went directly for Jack. Showed him a piece of paper. Jack went white. Sat down. Lit a ciggeret. Then he looked at me, waved me over. Shit. The man was a private detektive. Conner, he called himself. He had a statement from Charlie, explaning everything. Charlie couldn't take the presure. cause we had killed. For someone, blood is the limit. 
\\ \\
"I am willing to make a deal. I will not have you thrown in jail, if you accept." he said with confidence in his voice. "Anything." Jack said, with a insecureti in his voice. "You work for me. You do the things I can't do. You will never talk about me. We will communicate through letters." "And what is it you can't do, that we have to do?" I asked. "You? As plural? When did you become a part of this?" The moment you brought Jack in to this." "Well.. okay then..."
\\ \\
he explained, that he couldn't do surtain things, that would make hi job easier. Shuch as breaking an entry, stealing information, question suspectes with a bit of roughness. Anything that could potentially bit his ass. He'd pay us to do it. Money per job, where the sum would differ, depending on what job it was. "We accept!" Jack said, without much thought. I just agreed with Jack, as a job working together, would make us closer.
\\ \\
Me and Jack's relationship grew. We almost always had a little chat, when we met at the bar. He started giving me drinks, from time to time. I noticed him stalking me, from where ever he was sitting. Always keeping a eye on me. Threating the men, who tried to woo me. Of course, when I wasn't around. 
\\ \\
One day Conner showed up at the bar. Drunk. One ciggeret in the hand and another from the mouth. Stubbling through the room. Directly at Jack. Started mumbling about his lonelyness, as his wife had left him. Eventually, she came back, but as of the time, he was left alone. He fell asleep. Jack carried him outside. I followed. "Im taking him back to my place. See ya' later alligator" "Hopfully sooner than a while, krokodille." What a stupid thing to say! I was cringing, as he walked away.
\\ \\
Jack didn't show up at the bar for awhile. He didn't contact me, revolving any jobs. It was like he'd disapeard. One day I got a letter. "Come to Greenville, Sunday the eight of Janurary. 7 p.m. at "The Sirens Collection". Jack." I went there. Jack and conner where sitting at a table. Red lights everywhere. Leather sofas. An weird area, that looked like it had been an outdoor area. 
\\ \\
This letter thing isn't working anymore. I need information in detail, I need it through words. The jobs will still come as letters, but when the job is done, we'll meet here. I lit a ciggeret. Looked at conner. Looked at jack. Looked back at Conner. nodded. They then invited me to the table. There was a skinny bitch. A joke from Jack. I threw it in his face.He kicked my leg, so hard, that when I went to get a Bloody Marie, I stumbled.
\\ \\
As the day past, and we did job for Conner, I started to hint, that Jack should take me. Sexually. Hard. At home, the bathroom, an alley, anywhere. After a few days of interigating a man, he picked up on the hint. We went to his place. 
\begin{center}
	\large\textbf{7. Blood dripping from my scars \newline on my face and in my soul}
\end{center}

A dump. It had its charm, but a dump. Trash and cloths everywhere. Only the absolutely necessary furniture. A bed. A TV. A small table. A microwave. And a tower of pizza boxes. He fucked me. every place. The tower went down. The bed almost cracked. The TV fell on the floor. After a little fucking, he started getting rough. He tore my back, slaped and spat in my face. Twisted my nippels, so hard, they almost fell of. Domination. I liked it.
\\ \\
This went on, for a long time. We did small crimes together, worked for conner, fucked and drank. I was thrown out of school. Stopped all contact with my family.  He was exited one day. He said "This is the day Jill!", as he showed me a pack of white powder. We wnet to the bathroom. I was snorting coke. What a feeling. This became a daily rutine. Snorting and snorting, to my nose was hurting. We started selling coke, for money, to buy more coke. Later LSD, mushrooms EMDA, everything we could get our hands on. 
\\ \\
One day Jack and I was tripping hard on LSD, as Jack's trip became bad. He went to the kitchen, and grabed a knife, and some string. He tied me up on the bed. used tape, so I couldn't move my head. Not one cm. He stated cutting down my face. One stripe. Wto stripes. he went on. Blood everywhere and screams. When he ment he was done, he left the appartment. He left me tied up. I was lying there for one and a half day. 
\\ \\
He finally came home. No memory of what had happend. He untied me. I kissed him. I loved him. he could do what ever he pleased. But everything has an end. 
\\ \\
After some time, doing small crimes, a man busted us. A private detktive called Conner. We never got his full name. Conner stuck a deal with us. if we helped him, he wouldn't turn us in. he'd even pay us for doing it.
\\ \\
He robbed a grocery store, without me. He was busted. He had to sit in jail, for two and a half year. When he came out, he was a new man. No drugs. No drinks. nothing One day, he was gone. He had set fire to his apartment. Everyone thought he had died. I didn't. I knew him. I had dokuments. Well, I knew where to find his dokuments. And it's for surtain that Conner had helped him. So that's where I would start. At his new home in Greenville.

\newpage

\begin{center}
	\large\textbf{8. My hunt of love and eventually revenge}
\end{center}

I still had the money from the roobery. I used it to buy a house in Greenvile. A big house. I started surducing men. Lying, misleading, taking them away from their lonlyness, just to fuck them over, and destroy them. One day, one woman was sitting on a bench, in the park. Crying. Something made me go to her. "What's wrong, love?" it had been so long, since I har felt compassion. "I've been broken. Broken once again. Men. I let them in, only for them to ruin me. everything I fought for. Everything I've become. Me. They destroy me. Again and again and again and again AND AGAIN AND AGAIN AND-" "Love, I got it. Stop yelling." "Sorry, I'm just vurnable at the moment. Im emotionally broken."
\\ \\
As I was sitting with this woman, I realized I had the perfect oppertunity to heal her. Use my gifts, so she can destroy the gender, that had destroyed her so many times before. This was when my cult of sirens started. To start with, it was only harmless seducing. But after awhile, it wasn't enough. We needed more.
\\ \\
At the time we were five, including me. Marsha, Christine, Beatrice and Juliana. One surgested a bond. Something we had, that made us special. I knew just the thing. I washed my make-up of, to reveal my face. My scars. I picked up a knife, and said "Stripes. Scars. A scar that showes, beneath our appearance, we are scared. Scared by all the men who have been useing us. Three of the four women agreed. Christine didn't. I threw the knife at her. I hit her throat. She died in just a few seconds. 
\\ \\
Everyone was in shock. The women was looking at the women. The blood. Then at me. Beatrice then said: "This is what we should do. Kill the men. Cause the men killed our insides. Our feelings" she said with such a calm voice. "How should we do it?" Marsha asked. "You ever heard about mermaids? Or perhaps sirens? We will be like sirens." I cut their faces with the knife. Afterwards a light shined from our scars.  
\\ \\
My three sirens where lifted. Their skin color, their hair color, their face, everything about them changed. They became beautiful. Almost as beautiful as me. A voice started singing. Tim Buckley's song. "Song to the Siren". I startede to sing along. We all did. It was the most beautifull harmony. Voices like angels. My dear sirens where now truelly sirens. We bought a house. Painted it with images of boats craking, men falling overboard, and taken to the depths of the sea.
\\ \\
My desiples went out doing nights, mostly in the weekends. Took turns. brought back a man. We plesuared him. We desived him with food, singing, sex, everything a man loves. Brought him to the river. Through him in. Our voices would paralize our victims. They drowned. Our cult kept growing. Our powers became greater and greater. We were the justice of women. One day an ark came floating, as we had just thrown a man in the river. We went on board. it was for us. Inside it there were a bed. Pictures of greek mythological creatures. One of them was of us. Everytime we got a new member, the picture changed, and she would appear on it.
\\ \\
I'd completly forgotten about Jack. But one day, I walked down Streaker street, as I was going to Adam's Apple's, the organic vegetablesshop. I saw him. Jack. he didn't reconize me. It had been so many years since I had seen him. There he was. Strolling dowStreaker street, number 42.

\begin{center}
	\large\textbf{8. The hunt of love and eventually revenge}
\end{center}

I stalked him. He had a girlfriend. A normal job. He wasn't smokeing, and only drank rearly. And never at bars like The Sirens Collection. He had gotten an normal life. I was broken. I needed revenge for what he'd done to me. He'd left me. Either he had to come back to me, or he had to disapaer. Once again. 
\\ \\
I didn't fit into his new life. So he had to disapear. First, I needed him, alone, at a bar. A man can be broken hearted aswell. So I went for the girlfriend. I needed her to leave. So I sent some pictures of me and Jack fucking. She was the type who would just leave. She wouldn't mention it. Atleast, I hoped so. It worked. 
\\ \\
Jack went a bar. I sent in Beatrice. And then left. I said to my sirens, that they would have to do this one without me. i went to the ark, and waited. They arrived. They did what they always do. And then he fell into the water. They left. I couldn't let him die. I went on board of the ark. Pulled Jack up from the water. he looked at me. He reconized me. He said "You!" with a terrified tone in his voice. I didn't know what to do. I pulled out my knife. The one we used for rituals. I stabed him. "Who made me do this?" he said, as he was dying. "You. You did. It was always you! You made me like this."

\end{document}