\documentclass[]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amsmath,amssymb,stackengine,xcolor}
%opening
\title{I}
\author{Andreas S. Erslev}
\renewcommand{\abstractname}{I}
\begin{document}

\begin{center}
	\Large\textbf{I}
\end{center}
\begin{center}
	\large\textbf{Andreas S. Erslev}
\end{center}

\begin{center}
	\large\textbf{1. I}
\end{center}

To whom it may concern, for those willing to listen and the few, who has nothing better to do, I'd like to tell a story. The whole ordeal started an early morning, just about 7 a.m. Nothing seemed strange, as I got out of bed. A small dark bedroom, with just enough space for me to work thorughout the day. After booting up my old dusty, trusty computer, brightening the room with eyesoring ember pixels, I drag myself, blinded by my eyelids and the embers ash, to the kitchen. A small kitchen. Just enough room for one and a half man. Fine it was, since cooking hours was my sanctuary doing the 24. Start my morning making the same discount instant coffee. Rituals. Traditions. It makes the early day easier. The next two for the forenoon. Et cetera. 
\\ \\ 
With the coffe in my hand, the journy continued to the bathroom. Coffee, again, makes this easier. Flush out the body, the events of the preivous day and the nightmares of the unconscious dusk to dawn. For my next ritual, I wander to the livingroom, trying to collecet the last pieces of myself, as the last sip of cold coffee fills my mouth and mind, so the day can finally begin. I end up sitting in the same chair. Recurrence. Reiteration. A comfy chair no one ever really uses, since it isn't that comfortable. But I'm used to it. It was my first piece of furniture witch made it have a nostalgic aroma. Picked up on the curb. I slowly wake up. Caffeine through the blod and springs in the arse. It's going better than normal, better than expected. Yesterday was a late night. Just like so many others. Habits. Patterns.

\newpage

\begin{center}
	\large\textbf{2. She and I}
\end{center}

She didn't even notice me, as I arrived home. She's used to it. I, however, unfortunately, always notice the cliking sound. A noice from the bedroom. The commotion she likes to wake up to. I'm mildly annoyed. She was a black magic woman, with bleached hair. She has big lips, lovely for a kiss. Cheaks was round, just like a red apple. Shapes like a natural woman, like a green pear. A bit extra kilos, but that never really bothered me. Eyes were brown... I think. They never really captured my attention. I never got lost in stool brown labyrinths. 
\\ \\
As I sit, as she occupies my thoughts, my mind starts to wander. The noicy cliking becomes a meditative inspiration, instead of an annoyance. My eyes wander through the room, as I notice things I've never noticed before. A black spot on the ceiling, right by the corner. A red light from the sun, bouncing of an grotesque painting of a whale down-under. My father gave it to me. A dying plant, beyond saving. My mother gave it to me. A few cobwebs, dangling around. The dust became noticeable, through the beems of light. A letter on the table. A table I inherited from my grandfather. He cut it himself. Chippings. I start to become a part of the room, as the clicking goes on. My sense of being disappears. 
\\ \\
The clicking stops. Abruptly. I start existing again. Unexpectedly. I move towards the table. I look at the letter. She wrote it. I look in the letter. She ment it. It's over. A notice of the end. Soundless I whisper "It can't be real, wake up you buffoon", as i'm softly wacking myself, with a banana, that was lying in the fruit ball she made. It was the only thing she had in the apartment. She could take ownership of it all, it wouldn't matter. All I wanted was the love of my life to come back, so I could lay eyes upon my lover, one last time. So I could say goodbye. So we could part ways in a proper manner. Underneath the letter there is a carving. It says "I loved you. Never forget that". A tear presses it's way through my tear ducts.

\newpage

\begin{center}
	\large\textbf{3. Her, She and I}
\end{center}

Days passed, and I couldn't seem to get myself out of my head. I can't take it anymore. Destination, "The Flirtatious Succubus". Tempted to do the one thing, i promised myself not to do: Buy a pint. One pint, that leads to another. It makes the evening easier. The next two for redemption. Et cetera. Russian cocain burning. I've been to the pub pleanty of times, but never alone. Never alone at this pub. Never alone in this era. Alone at a pub. How pathetic. It's a dangoures game. Russian roulette gambling. One after the other. Lime burning through my teeth. I. Alcohol. Twighlight thought trainwreck. Lonlyness getting stronger and heavier for each sip. A darker twighlight. Only acknowledged by a cat, who has claimed ownership of the pub. 
\\ \\
A women with a stripe down her face, starts singing, as she slowly dances, with out my knowlagde, closer and closer. Seducing every man. Jaloux making all women. I light a cigarette, even though I already have one. It's almost done, I say to my self. My glance becomes split, as I for a short moment see 4 ciggarets lying next to eachother. Two a newly born embers and the others on brink of death. The complete circle of life. Maybe I should start over. Again.
\\ \\
The woman is comming closer, and I start to notice her outcry of attention. It suits me. I slowly move in a 180 degrees movement, and smell a fragrance so delightful, it cancels out all other senses, for just a shot moment. I see her. My senses are canceled out, by the sight of her. She's standing. Dancing. A completly pale body, that seemingly hasn't seen sunlight in ages. Black hair, that incapters the light, and gives of a special glow. Her essence is sexy, but yet so classy. Her eyes. Oh her eyes. Soft, smiling, but yet direkt and cold. Like a blue ocean, where a sailer gets lost, with the knowledge that somewhere, out there, something is worth dying for. Her mouth was smiling, like there where a seacret on her lips. A soft smile. But a trained one, that could be givin, even at a funeral. Her face collects all of her facial expressions, which is fed into a whole. 
\\ \\
I don't remember her body at all, maybe beacuse of the alcohol or maybe because of her captivating face. This woman has already forfilled my needs, with just a song, a dance and a mesmerising stribed face. What a woman.

\newpage

\begin{center}
	\large\textbf{4. Them, Her, She and I}
\end{center}

As I sit at the bar talking, while she's sitting at the bar listening, my mind slowly forgets about my loved one, as the monolog becomes more and more about my passion than my sorrow, as im slurping my way through pints upon pints and a white russian. It was like the only sense that made sense, was the ability to speak. I had a connection with this human being, that I'd never experienced before. After awhile, she surgests a change of surroundings. I agree instantly. whatever stage she wishes to act upon. 
\\ \\
We walk through town. The town is like many others. Shops, pubs and streetlights. As we walk in the cold winter wheather, with new snow slowly faling beautifully from the sky, laying atop of the roads as a blanket, she starts to sing. A spellbinding song. A song of a siren. I can't smell or see or talk or touch or taste or think or feel. I can only listen. My body goes to autopilot. I just walk, as she leads me with her voice. 
\\ \\
The singing stops. We stop. I start existing again. I feel a cold breeze. It's a hosue. The house is painted with graffiti. Waves, splassing togehter and boats cracking, sinking into the deapths of the unknown water. There is a piece of wood, from what appears to be from an old boat. The piece of wood tells me, that the house is named Odysseen. She takes me inside. The song that she was singing, arises again and becomes plural. The voices brings me to a livingroom, where there are anchors, rudders and ropes on the walls. A small fireplace crackles a rythem, as a clicking noise. A short dangerous thought of my earlier loved one.
\\ \\
There are 13 women, all singing and slowly dancing. They all have the same captivating glance in there eyes, as the woman who lead me here. They all have the same pale color of skin, some with black frizzies and others with long blond hair. All with a stripe down their face. They all look so alike, and yet, so different. They placed me in a chair. So comfortable. I have never experienced something like it. They gathered around me, still singing and dancing. Slowly they start touching me. Caressing and massaging. I close my eyes, and my sense of touch slowly returns. It feels like i've absorbed pills. This must be heaven.

\newpage

\begin{center}
	\large\textbf{5. You, Them, Her, She and I}
\end{center}

Some bealive that before trancending to the metaphysical, you need first to experience the one, before the final, so you know the difference. The outcome of your physical lifestyle. I sit there, slowly drifting to a meditatively dream state, becoming one with the room. They stop singing. Abruptly. The song must have endend. Unexpectedly. Im back. They aggressively drag me out of the chair, as if I couldn't do it myself. I realize, I couldn't do it myself.
\\ \\
I hold my head clear. I don't know what's going on anymore. Or where I am. They start singing again. I try to fight it, but the trance slowly starts to come back. I start thinking of her. I start to miss her. Sorrow fills my eyes. A tear presses it's way through my tear duct, as I get lost in the memoy of her big,  cocoa brown eyes. The 13 women look at the woman who lead me here, judgmentally and disappointing.
\\ \\
I'm once again one with the room. I'm an object. I can't move. They move me around. They feed me. The best tasting food I've ever sensed. My tastebuds overtakes my body. I only sense the morsels danicing on my tongue. They take me to a bedroom. Even though I haven't finised. They strip me down, from toe to top. I let them. As a sexual journy is about to begin, they stop singing. A soundless sexual experience. With closed eyes, it becomes intence. They stop. Even though I haven't finised. For a short while, im back, wondering about the near future. They start singing again. 
\\ \\
I am in their possession. I am their puppet. They move me through the streets. There isn't a soul in our path. There are no lights in any of the houses. The lights from the sky is pleasent, like the sun is shining in the twilight. It has stoped snowing. Every footstep I take, should have ruin the beautifull snow blanket. Nothing happens. The snow stays intakt. We get closer to the towns river. On the river there is a ark floating at berth 13. Nothing but the ark. Usually there are full of other boats. We board the ark. The water was frozen. The ark was stuck. The singing intensified. It seems as if I'm now free. Finally free. But I don't want to. I stay on the ard. I'm keeping myself in their basement in Stolkholm. 
\\ \\
As I stand on the very eadge, looking at the ice, it slowly starts to melt. It seems, as if the song is evaporating the icy river. Slowly a pitch black pit is forming. They finish what they Started. Again soundless. As I climax, a knife runs down my face. There is no blod. Striped naked, I suddenly start walking. Slowly thowards the hole in the ice. Without resisting, just moving slowly, and slwoer and slower, til stoping is near. I jump in. It's warm, comforting yet terrifying. The singing stops, as i slowly start sinking, like the boats on Odysseen. I see the women leaving. I try to swim, but my movement still feels out of my control. Im drowning. Suddenly a hand appers. It grabs me. It pulls me. Out of the water. Can it truly be? Is it? It was you.

\end{document}
