\documentclass[]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amsmath,amssymb,stackengine,xcolor}
%opening
\title{An Anecdote}
\author{Andreas S. Erslev}
\renewcommand{\abstractname}{An Anecdote}
\begin{document}

\begin{center}
	\Large\textbf{An Anecdote}
\end{center}

\begin{center}
	\large\textbf{Andreas S. Erslev}
\end{center}

\begin{center}
	\large\textbf{1. A Dead Man Calling}
\end{center}

*Ring Ring*... *Ring Ring*... The phone screamed, like a madman, with an empty bottle of looney pills. *Ring Ring*... *Ring Ring*... In the middle of the night, like a newborn suffering from colic. A flash of PTSD went past my eyes, as I dozily answered and said "Who's visiting at this time?" with a bit of frustration and a pinch of confusing in my voice. "Yes, apologies Mam, uh, um, a situation h-has arisen. Eh, Another m-man has been, um, found down by the r-river." a insecure voice, possibly Jerrys, mumbled. "Another one has drowend, eh?" I said, as a yawn was approaching. "Well.. eh, not, um, exactly... It seems as i-if he WAS in the water, Mam, but his final resting place, is a-aboard the ark at berth 13." My curiosity woke me, faster than a tuned scooter on the highway. "Well... Are you gonna tell me how he'd died, or do I have to wait for the moning paper?" my curiosity spat out. "Well, eh, Mam... he was staped.. um, twe-twentyseven times. He was found next to a post-it note, saying Jill. He has cuts down his face, like the others, however, he has many more" a more confident voice said. "I'll be there in a jiffy." I said merrily, as I struggled with my socks and rushed for the door.
\\ \\
I approached the ark at berth 13. The whole squad had already arrived. Everybody stressing around. Coroners taking pictures from all angles. Journalists and policemen screaming at each other. One young man puking in a bush. "Have they never seen a bloody body before" I quietly said out loud to myself. 
\\ \\
The ark was magnificent. I have always admired it. I've never seen the owner. He kept it in good condition, no mater the weather or time of year, it always looked as good as new. I always wanted to see what was inside. Now I got to see the inside, of the magnificent construction. Sadly, there wasn't much to see. What a pitty. A pitty indeed. Some awfully grotesque pictures on the walls, a beautifully made queen size bed and an old wooden desk. A bit of the wooden floor was missing. The pictures resembled different types of greek mythical creatures, such as Catoblepas, Minotauros, Centaurs, Sirens, Cyclops, Medusa, the list goes on. One pictures stood out. Not as hideous as the others. Medusa and Sirens merged together.

\newpage

\begin{center}
	\large\textbf{2. Life Like Figures On A Crime Scene}
\end{center}

A blue sky slightly covered with clouds. The sun, lightly shining through. You can almost feel, how they spread the heat on the green field in the background. The moon exposed itself, behind the clouds, in the far corner. In the middle of the painting Medusa is standing. Posing dominantly. Her snakes billow in every direction. A nimbus surrounding her head. A knife in her hand, with red blod dripping. Her face has blue blood running down, from top to bottom. In the far background you can see a figure standing. If you look really close, you see him standing, laughthing, also with a knife in his hand. Dripping blue. It is as if you can see a resemblance to the man lying dead. Peculiar.
\\ \\
The bed had a golden frame, gleaming rays of joy, from the sunny side, and shades of darknes from the moons side. The maddras looks  comfortable, one could wish that, if they could choose it would be a nice, final, resting place. The blanket. Looking like a cloud that had descended from the sky, and would slowly cover you, from toe to top. Two pillows, that has an alikeness to a womans bosom. Lying comfotably at mothers breast. Safe and sound. Sleeping like a baby. It look as if a man was lying in the bed. But he had no face. Instead there was a mirror. I saw myself. As if I was lying in the bed.
\\ \\
Around the bed, women was lying, caressing, prying to the man in the bed. It looked as if they were all singing. Properly a loliby to make one sleep. All the women where so beautifull. In their on distenkt way. But yet, they all seemed so alike. On the side of the moon, where the dark light shined, the women had long, blond hair. It shined so bright. On the other side, the darkness rulled in the womens eyes. Dark hair and pale skin. Again, a contrast to the suns bright rays of ember. A panoramic view, from dark to light. The sun and moon walked from left to right. The women from the right to the left. In the middle the sun and moon collided. Right where Medusa was standing. They all had their own distinkt cut down their faces. with blod running from it. 

\newpage

\begin{center}
	\large\textbf{3. Tales From Witness Investigations}
\end{center}

He was lying on the floor. There was a blood trail, from the bed towards the desk. He had a cut. A stripe. He had a cut from toe to top. He was stapped in the heart. twentyseven times. He had been able to fumble his way to a desk, getting a post-it note, and written a name. "Jill" it said. He was lying there half naked. The body was frozen. Totally stif. Lying in a pool of purple blood. His eyes seemed peacefull. As if he had gotten a burden of his shoulder. As if, it had been a justified murder. As if, he owed something to the murderer. Owed his life. A lot of information can be obtained, by looking at the gleam, from a dead mans eyes. A story of death.
\\ \\
When it comes to murder, there is one thing, that you can always be most certain about. A private investigator will show his face. This time it was old Conner. Good old mister Finitis. "Hi Conner. What are you doing here. Aren't you supposed to be retired? Maybe go for a round of golf." I said with a resignedly voice. "Ha, well old chump, I properly should. I properly should. But it's hard. Stop smokeing. Stop drinking. And now, basically, stop thinking. I couldn't stay away from a good, juicy murder case and you of all people, should know this." he said a avid tone. He seemed sincere, yet with a ulterior motive. I told him what I could tell him. He told me that he had known the feller, in another life. He had helped him with a case or two. Yet, he didn't have much to say about him. Except that his name was Jack. Jack Mojoson. He said he knew nothing of this "Jill".
\\ \\
He went with me, as I went from house to house, asking what people had seen. It was good with a bit of company, and the old geezer was in the end, A good detektiv... in his earlier years. Most had slept through the night. Hadn't seen or heard anything. But one old man, who slept doing the daytime, and watched TV at night, had seen something. Matter of fact, he'd seen something several times. A group of women, singing the same song everytime, leading a man abord the ark. After some time, the women would leave the ark again. In silnce. He never noticed any male individuals leaving the ark.
\\ \\
Yesterday was different. First of all, one woman was missing. The one, who normally leads the group. The one with billow hair. There were another perculiar event that night. After the women had left, a woman was seen boarding the ark. Shortly after, she came down again and left in a hurry. 

\newpage 

\begin{center}
	\large\textbf{3. Scenes From Surveillance}
\end{center}
 
These informations were worth my yearly pay. Finally we had a clue of what happend at night. Earlier we couldn't set up night control, since we didn't know where along the river the men would fall in. It is a pretty long river, you know! But now it seems, as if there were some sort of cult. And it all revolved around this ark. I parted ways with Conner, and went back to the staion. The first thing we did, was setting a surveillance squad in practise. The next thing, waiting. With a cop of tea, and some biscuits.
\\ \\
Wedensday, Day 1: 
\\
A drunk man slept on the ark
\\ \\
Thursday, Day 2: 
\\
A man peed from the ark. Also, a bit on the ark.
\\ \\
Friday, Day  3: 
\\
No events, revolving the ark. We, however, busted a drug dealer.
\\ \\
Saturday, Day 4:
\\
First it seems as an normal evaning. Untill somethings happening. A group of women are, walking, singing and leading a man through the streets, next to the river. We do not see a woman with billow hair. If the old man speaks the truth, she must be missing again. behind them, someone is following. We zoom in on the individual. Dear god, it's that old geezer Conner. How did he... No matter, his knowlagde will soon be ours. The women walk onto the ark. It looks as if they are having sex. All surrounding the male individual. Like in the painting. After a while, they start singing. It seems as if the ice on the river starts to melt. The man jumps in. Slowly the ice returns. The women leave. Conner boards the ark. He just stands there, looking. Then leaves. As the man, presumably are drowning, a red light is shining from beneath the ice. 

\newpage

\begin{center}
	\large\textbf{3. Missing Accused Witnesses}
\end{center}

We had to find out what all this was about. The note, the cult, The dead man Jack, Conners involvment and this Jill. The next few days went by, as we looked up everyone called Jill in town, tried to match their profile and their wherabouts. 
\\ \\
We also tried to get in contact with Conner, but after the night at the ark, it seemed as if he had disapered. He wasn't at home, non of his friends or neighbors had seen him. Not even his wife had any clue. We checked travel companies, car rentals, train tickets, everything he could have used to get out of town, but nothing in his name. 
\\ \\
Jack was alot easier. We had a full name and a face. We quickly found his appartment, his friends and his ex-girlfrind. The odd thing was really, that we could only get information about him that had happend the last five years. We couldn't find any family. All his friends met him at that time, or later. His girlfriend only knew him for about 3 years. He was hired at his job, as a computer programmer four and a half years ago. His appartment, at Streaker street 42, second on the right, was the oldset information we had about him. Not even his name gave any information, as if he had resurrected from another life. 
\\ \\
It all seemed as a true mystery. An unknown woman who seem to possibly be a, well presumably, cult leader. A retired detektiv gone from the surface of earth. A man raised from the ground.
\\ \\
Next thing we had to, was to go and interview 27 Jill's, where one of them, hopefully, would be the right woman. In the days that had past, only 2 Jill's where dokumentet to departer from town. Hopefully, she wasn't one of them. We narrowed it down to be 4 Jill's, based on alibi's. Jill Brown, Jill Clinton, Jil satsuki and Jill Absalon. Now we had to interview them proper.

\newpage

\begin{center}
	\large\textbf{4. Stories From Indifferent Suspects}
\end{center}

Jill Brown: \\
Description: \\ Height: 167 cm. Weight: 59 kg. Hair color: Red. Age: 17 years. Adresse: Even Sirena road  28. Occupation: Student.
\\ \\
Tell me again, where were you Tuesday the second, the night of the murder? \\
I was at home. I watched a movie on Netflix, called 'The Little Mermaid', an old movie from disney. I love disney movies. After I watched the movie, I went straigth to bed at 10 pm! My parents came home around 10:30 pm. 
\\ \\
Do you know anybody called Jack Mojoson? \\
I don't. I do know a Jack Hanson, but no, not Mojoson.
\\ \\
Have you ever been at Streaker street, or in that area? \\
I've been at Adam's Apple's, the organic vegetablesshop, a few times. \\ \\
Conclusion: \\ She was a long shot. Seemed as if she told the truth. A bit young aswell. I quickly ruled her out.
\\ \\ 

Jill Clinton: \\
Description: \\ Height: 159 cm. Weight: 51 kg. Hair color: Grey/white. Age: 87 years. Adresse: Feles Chat du Gáta 17.  Occupation: Senior citizen.
\\ \\
Tell me again, where were you Tuesday the second, the night of the murder? \\
I was watching a political debate. I care alot about politics. It was a debate between Saul Bricc and Juan Raza. I, of course, was chearing on Saul Bricc. His values are the most importa- \\
Excuse me mam' we need short, to the point awnsers. \\
How rude! But if that is the premises. I watch the debate, from 7 p.m. to 8:30 p.m. I diden't leave the house. After this, I walked around the park. It was a quiet evaning. I came home about 9-9:30, and went straight to bed.
\\ \\
Do you know anybody called Jack Mojoson? \\
I don't know alot of people. You see, I'd rather spend my time taking care of my cats. I have 7 of them. All female. One of the cat's however is named Jack. I was supposed to have one male cat. It turned out it was also female. No kittens for me. Yet. She's named after my son. He was a disgrace. Doing crime, drinkg too much. I loved him. Even though I only saw him rearly. When he disapered five years ag- \\
Mam', please, just simple short awnsers! Let's move on. \\
Huh, well then, let's do so. But I will file a complaint about your attitude!
\\ \\
Have you ever been at Streaker street, or in that area? \\
Only at Adam's Apple's. 
\\
Conclusion: She didn't seem as if, she could do it. A 'sweet' old woman as her. And then with a ton of other women? No, she couldn't be the one!
\\ \\

Jill Satsuki: \\
Description: \\ Height: 174 cm. Weight: 93 kg. Hair color: Black. Age: 51 years. Adresse: Asiena Coolie-Chink Street  Occupation: . Origin: China.
\\ \\
Tell me again, where were you Tuesday the second, the night of the murder? \\
What? I welly do nut speake english vewy good! \\ \\
We need a translator! \\ \\
Conclusion: From what the translator told us, we could rule out poor miss Satsuki. She didn't have the looks, she'd never even been to Streaker street. She only knew people from the chinese part of town. At the night she was even working at Eve Pupillam Copia Scriptor, at the other side of town, a store selling fruits. From what she told us, mostly apples. It's odd to sell fruits at such a late hour. A mid-night healty snack.
\\ \\

Jill Absalon: \\
Description: \\ Height: 163 cm. Weight: 68 kg. Age: 59 years. Adresse: Huesos Rotos Road Occupation: Secretary at the school for vulnerable children. Currently on leave of absence, cause of a broken arm.
\\ \\
Tell me again, where were you Tuesday the second, the night of the murder? \\
Morphine. Lying in my couch, high as can be. My arm had just been broken sevarel places, the day before. I had to be operated. Full anesthesia.
\\ \\
Do you know anybody called Jack Mojoson? \\
No. I don't even know a Jack. 
\\ \\
Have you ever been at Streaker street, or in that area? \\ 
No. I live out on the country side. I only really come to town, for work. Our lifes, my husband and I, mostly takes place where we live. It's a small comunity, but that's how we like it.
\\ \\
Conclusion: All her information were correct. She had a broken arm, on the day of the murder. Dokuments show, that she actually were on morfin. I couldn't be her either!

\newpage

\begin{center}
	\large\textbf{4. Donuts And Tea At The End Of A Story}
\end{center}

Nothing worked. We couldn't find the right Jill, or anything about Jack and Conner. So we went to the last resort. The police's secret waepon. Adressing the public. We announced it all to the public. Only 3 hours later, we got a anonymous letter with a detailed deiscreption of a woman. It was with an adress, last name, detailed distreption of how she looked, really evrything we could have wanted. At the end of the letter, there were 14 lipstick kyssing marks.
\\ \\
We looked up the name, in our database. She had taken a plane to Denmark, from another city. She had bailed. We went to her house, to see if we could find some clues on how to find her. It was a basic house. Nothing out of the ordinary. But nothing that linked Jill to Denmark either. Then suddenly, one of my men, Mark, found a seacret door in the basement. A seacret room. 
\\ \\
Red lights. scented candels smoke, paintings of mythical creatures. Like on the ark. A bed. Haning above the bed, was the same painting of Medusa and the sirens. In the bed, the old geezer Conner was lying. Tied up. She had cut of his balls, choked him in fluids and left him for death. With a stripe on his face. Across from the bed, there was an altar. Candels all around of a picture. A picture of a man. A wooden carving saying "Jack" was haning. Beneth the picture was a box. Dokuments, photos, videos. All about Jack. Even his birth certificate. His real name, Jack Bosson. A former no life criminal. presumed dead. It said in our documents, that he had died in a fire at his appartment.  
\\ \\
I later read in the newspaper, that a woman, matching the description we got of Jill, had drowned in a river in Denmark, Aarhus. 

\end{document}
